Self-Supervised Transfer Learning From 2D Images to 3D Point Clouds

### 2022-04-13 doc/paper.tex
adds initial results for scannet with varying data amounts
updates instance supervised results
adds partial data results
Adds results from their implementation of point contrast

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c c c c | c }
                                        & ceiling         & floor          & wall           & beam           & column         & window         & door           & table          & chair          & sofa           & bookcase       & board          & clutter        & mIOU                    \\
            \hline
            Scratch                     & 90.34           & \textbf{96.84} & 80.63          & 0              & 25.5           & 56.95          & 62.93          & 75.14          & 86.21          & 65.77          & 72.12          & 76.91          & 56.4           & 65.06                   \\
            Supervised                  & \textbf{91.81}  & 96.74          & \textbf{84.11} & \textbf{0.21}  & \textbf{34.68} & \textbf{57.64} & \textbf{81.53} & \textbf{77.63} & \textbf{89.82} & \textbf{85.76} & \textbf{76.03} & \textbf{79.27} & \textbf{57.67} & \textbf{70.22} (+5.16)  \\
            \hline
            PointContrast               & \textbf{92.118} & \textbf{96.93} & 82.2           & 0              & 24.94          & 53.78          & \textbf{76.91} & \textbf{75.94} & 87.93          & 70.27          & 71.2           & \textbf{77.76} & 56.36          & \textbf{66.641} (+1.58) \\
            PointContrast - No Overhang & 91.624          & 96.86          & 82.02          & 0              & 29.37          & \textbf{57.5}  & 64.93          & 75.49          & 87.36          & 59.32          & 71.42          & 76.61          & 56.11          & 65.28 (+0.22)           \\
            CME \textbf{(Ours)}         & 90.8            & 96.57          & \textbf{82.52} & \textbf{0.110} & \textbf{30.94} & 56.94          & 68.71          & 75.12          & \textbf{88.48} & \textbf{71.7}  & \textbf{72.17} & 73.783         & \textbf{56.35} & 66.48 (+1.42)           \\
        \end{tabular}
    }
    \caption{S3DIS results using ContrastiveSceneContexts Code}
    \label{table:s3disResults}
\end{table*}

@@

\textbf{Pretraining on 2D:} Batch size of 64 image pairs where for each image pair we select 4092 pixels to contrast in our loss function. The loss function uses a tau of 0.4, a learning rate of 0.01, SGD optimizer with a momentum of 0.9, dampning of 0.1 and weight decay of 0.004. We decay the learning rate according to an exponential scheduler with an exponential rate of 0.99. Trained for ?? iterations.

\textbf{Transfer:} Transfer learning is done using the scannet dataset. We use a batch size of 8 and select 2000 point-pixel combinations per datapoint. The images are only center cropped to fit into the 2D model. The 3D model uses a voxel size of 5cm. The hyperparameters are the same al those in 2D except the learning rate is set to 0.1. It is trained for ?? time (I forget).

>>>>

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c c c c | c }
                                        & ceiling         & floor          & wall           & beam           & column         & window         & door           & table          & chair          & sofa           & bookcase       & board          & clutter        & mIOU                    \\
            \hline
            Scratch                     & 90.34           & \textbf{96.84} & 80.63          & 0              & 25.5           & 56.95          & 62.93          & 75.14          & 86.21          & 65.77          & 72.12          & 76.91          & 56.4           & 65.06                   \\
            Supervised                  & \textbf{91.81}  & 96.74          & \textbf{84.11} & \textbf{0.21}  & \textbf{34.68} & \textbf{57.64} & \textbf{81.53} & \textbf{77.63} & \textbf{89.82} & \textbf{85.76} & \textbf{76.03} & \textbf{79.27} & \textbf{57.67} & \textbf{70.22} (+5.16)  \\
            \hline
            PointContrast               & \textbf{92.118} & \textbf{96.93} & 82.2           & 0              & 24.94          & 53.78          & \textbf{76.91} & 75.94          & 87.93          & 70.27          & 71.2           & \textbf{77.76} & 56.36          & \textbf{66.641} (+1.58) \\
            PointContrast - theirs      & 91.97           & 96.67          & 82.4           & 0              & 17.84          & 56.49          & 75.39          & \textbf{77.63} & 87.35          & 63.3           & 73.53          & 79.55          & 58.76          & 66.22 (+1.16)           \\
            PointContrast - No Overhang & 91.624          & 96.86          & 82.02          & 0              & 29.37          & \textbf{57.5}  & 64.93          & 75.49          & 87.36          & 59.32          & 71.42          & 76.61          & 56.11          & 65.28 (+0.22)           \\
            CME \textbf{(Ours)}         & 90.8            & 96.57          & \textbf{82.52} & \textbf{0.110} & \textbf{30.94} & 56.94          & 68.71          & 75.12          & \textbf{88.48} & \textbf{71.7}  & \textbf{72.17} & 73.783         & \textbf{56.35} & 66.48 (+1.42)           \\
        \end{tabular}
    }
    \caption{S3DIS Semantic Segmentation results (mIOU)}
    \label{table:s3disResults}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.8\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c | c }
                                   & beam & column        & window        & door          & table         & chair         & sofa          & bookcase      & board         & clutter       & mAP@0.5              \\
            \hline
            Scratch                & 0    & 12.8          & 61.7          & 92.0          & 51.4          & 87.3          & 62.4          & 38.5          & 87.0          & 37.1          & 53.0                 \\
            Supervised             & 0    & 26.0          & 74.3          & 84.5          & 43.3          & 87.3          & \textbf{81.8} & 37.4          & \textbf{85.4} & \textbf{41.2} & \textbf{56.2} (+3.2) \\
            \hline
            PointContrast - theirs &      & 24.7          & 67.9          & 90.7          & 43.8          & 92.0          & 72.7          & 32.3          & 85.6          & 38.0          & 54.8 (+1.8)          \\
            PointContrast          & 0    & 17.4          & 68.2          & \textbf{93.0} & 45.7          & 88.5          & 63.6          & 34.1          & 82.1          & 38.2          & 53.1 (+0.1)          \\
            CME \textbf{(Ours)}    & 0    & \textbf{35.0} & \textbf{70.0} & 83.4          & \textbf{53.9} & \textbf{88.9} & 71.7          & \textbf{42.2} & 76.1          & 36.7          & 55.8 (+2.8)          \\
        \end{tabular}
    }
    \caption{S3DIS Instance Segmentation Results (mAP@0.5)}
    \label{table:s3disInstanceSegmention}
\end{table*}

\begin{table}[t!]
    \centering

    \begin{tabular}{ c | c c c c c c}
                            & 5\%  & 10\% & 20\% & 30\% & 40\% & 100\% \\
        \hline
        Scratch             & 56.9 &      & 64.1 &      & 65.6 &       \\
        \hline
        PointContrast       &      &      &      &      &      &       \\
        CME \textbf{(Ours)} & 60.8 &      & 64.8 &      & 64.7 &       \\
    \end{tabular}

    \caption{Scannet Semantic Segmentation with Partial Data  (mIOU)}
    \label{table:scannetVaryingDataAmount}
\end{table}

% \begin{table}[t!]
%     \centering

%     \begin{tabular}{ c | c c c c c c }
%                             & 5\% & 10\% & 20\% & 30\% & 40\% & 100\% \\
%         \hline
%         Scratch             &     &      &      &      &      &       \\
%         \hline
%         PointContrast       &     &      &      &      &      &       \\
%         CME \textbf{(Ours)} &     &      &      &      &      &       \\
%     \end{tabular}

%     \caption{S3DIS Semantic Segmentation with Partial Data  (mIOU)}
%     \label{table:s3disVaryingDataAmount}
% \end{table}

@@

\textbf{Pretraining on 2D:} Batch size of 64 image pairs where for each image pair we select 4092 pixels to contrast in our loss function. The loss function uses a tau of 0.4, a learning rate of 0.01, SGD optimizer with a momentum of 0.9, dampning of 0.1 and weight decay of 0.004. We decay the learning rate according to an exponential scheduler with an exponential rate of 0.99. Trained for 20k iterations.

\textbf{Transfer:} Transfer learning is done using the scannet dataset. We use a batch size of 8 and select 2000 point-pixel combinations per datapoint. The images are only center cropped to fit into the 2D model. The 3D model uses a voxel size of 5cm. The hyperparameters are the same al those in 2D except the learning rate is set to 0.1. It is trained for 20k iterations same as pre-training on 2D.
